---
title: "Combination Document"
author: "Haotian Zheng"
date: "3/10/2022"
output: html_document
---

***This document is meant to combine the output data of padloc, defensefinder and crisprcastyper.***

*Aim to:*

1. Get the output of the softwares.(By using shell or python command in linux envs.)
    + Padloc data.
    + Defensefinder Data.
    + Cctyper Data.
2. Modify three final output file, prepare for the combination.
    + Padloc data.
    + Defensefinder Data.
    + Cctyper Data.
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggrepel)
library(RColorBrewer)
library(ggpubr)
library(plyr)
library(reshape2)
library(pheatmap)
library(RColorBrewer)
library(readxl)
library(dplyr)
library(tibble)
library(scales)
library(ggthemes)
library(igraph)
library(psych)
library(vegan)
library(tidyverse)
library(knitr)
do.write <- F
options(scipen = 200)
```

### Get the output of the softwares.
#### padloc
*Note: Using the v1.1.0 version padloc database, with the plsdb.fna as an input, the padloc can only using sequence under 32000000 for training, so split the origin database, run the padloc.*
```{bash,eval=FALSE}
# Step 1: split data.
num1=1;num2=0;num3=0; while read line; do let count++; if [[ $line == \>* ]]; then echo "Starting with >, the sequence number is $num1, and the sequence line is `echo $count`"; num1=`expr $num1 + 1`; if test $(($num1 % 200)) -eq 0; then num2=`expr $num2 + 1`; num4=`expr $count - 1`; echo "Each file contains 200 plasmid seuqences, and the file number is $num2"; head -n ${num4} plsdb.fna|tail -n +${num3} > splitted_files_under320000/SeqSet_${num2}.fna; num3=`expr $count + 0`; fi; fi; done < plsdb.fna

# Step 2: run all split fna files in batch.
find *.fna | parallel -j 15 -I% --max-args 1 padloc --fna %

# add tag into .padloc.csv files and combine the .padloc.csv files.(can use r to merge the files. just sometimes the file number is really large.)
# (add updated code here.)

# count fasta files length.
## Step 1:
awk '/^>/&&NR>1{print "";}{printf "%s",/^>/ ? $0"%":$0}' plsdb.fna > plsdb_one_line.fna
## Step 2:
awk -F"%" '{print $1"\t"length($2)}' plsdb_one_line.fna > plsdb_one_line_count.fna
```

#### defensefinder
*Using the padloc .faa result, then run defensefinder in batch.*
```{bash,eval=FALSE}
# run the defensefinder in batch.
find *.faa | parallel -j 10 -I% --max-args 1 defense-finder run -–dbtype gembase %
# run the prodigal to get the position of proteins in the sequence.
find *.fna | parallel -j 5 -I% --max-args 1 prodigal -i % -o %.genes -a %.proteins.faa -p meta
```

#### cctyper
*Using the plsdb.fna.*
```{bash,eval=FALSE}
cctyper plsdb.fna all_plasmid_result
```
---


### Modify three final output file, prepare for the combination.
#### padloc
```{r,warning = FALSE,message=FALSE}
# read files in batch and add tags.
padloc_sepfiles <- list.files("../Results/1.Original_Data/1.padloc_data/csv_results/")
padloc_dir <- paste("../Results/1.Original_Data/1.padloc_data/csv_results/",padloc_sepfiles,sep = "")

outdir_addtag <- "../Results/1.Original_Data/1.padloc_data/csv_results_tag/"
dir.create(outdir_addtag,recursive = TRUE)
outdir_dir <- paste(outdir_addtag,padloc_sepfiles,sep = "")

for (i in 1:length(padloc_dir)) {
  new_data <- read.csv(file = padloc_dir[i], sep = ",", header = T)
  new_data$filenumber_tag <- i
  write.csv(new_data, outdir_dir[i])
}

# combine all the files.
merge_data <- read.csv(file = outdir_dir[1],header = T)
for (j in 2:length(outdir_dir)) {
  new_data2 <- read.csv(file = outdir_dir[j], header = T)
  merge_data <- rbind(merge_data, new_data2)
}
merge_data <- merge_data[,-1]
merge_data$specific_tag <- paste(merge_data$system.number,merge_data$filenumber_tag,sep = "_")
length(unique(merge_data$seqid))
if(do.write){
  write.csv(merge_data,"../Results/1.Original_Data/1.padloc_data/padloc_origin_output_fromR.csv",sep = "\t",row.names = F)
}
```
**The padloc output have `r length(unique(merge_data$specific_tag))` different defense systems in `r length(unique(merge_data$seqid))` plasmids.**

#### defensefinder
*Add the protein position from prodigal to the output of the padloc.*
*need to change something into the right shape.*
*should add some update scripts on it.*
```{r,warning = FALSE,message=FALSE}
# Import Data.
definder_origin <- read.table("../Results/1.Original_Data/2.defense_finder_data/defensefinder_origin_output.tsv", header = T, check.names = F)
protein_name1 <- read.table("../Results/1.Original_Data/2.defense_finder_data/find_the_position/split_protein_name1.txt",header = T, check.names = F)
protein_name2 <- read.table("../Results/1.Original_Data/2.defense_finder_data/find_the_position/split_protein_name2.txt",header = T, check.names = F)
protein_name3 <- read.table("../Results/1.Original_Data/2.defense_finder_data/find_the_position/split_protein_name3.txt",header = T, check.names = F)
protein_name4 <- read.table("../Results/1.Original_Data/2.defense_finder_data/find_the_position/split_protein_name4.txt",header = T, check.names = F)

# Add site imformation into the defensefinder output.
combined_protein_name <- rbind(protein_name1,protein_name2,protein_name3,protein_name4)

combined_protein_name_beg <- combined_protein_name[c(1,2,4,5)] %>% rename(sys_beg = protein_id, id_info_beg = id_info)
combined_protein_name_end <- combined_protein_name[c(1,3,4,5)] %>% rename(sys_end = protein_id, id_info_end = id_info)

site_merge_beg <- left_join(definder_origin[c(-5)],combined_protein_name_beg)
site_merge_end <- left_join(definder_origin[c(-4)],combined_protein_name_end)

site_merge_combine <- cbind(site_merge_beg,site_merge_end)

site_merge_combine2 <- na.omit(site_merge_combine)
site_merge_combine3 <- site_merge_combine2[c(-11,-12,-13,-15,-16,-17,-19)]


site_merge_combine3$site <- paste("(",site_merge_combine3$beg,",",site_merge_combine3$end,")")
site_merge_combine3$length <- site_merge_combine3$end-site_merge_combine3$beg

if(do.write){
  write.table(site_merge_combine3,"../Results/2.Combined_Data/Process_file/2.defense_finder_data/defensefinder_addedsite.txt",sep = "\t",row.names = F)
}
```
**The DefenseFinder output have `r length(site_merge_combine3$sys_id)` defense systems in xx plasmids.**


#### cctyper
*select the CRISPR_Cas.tab, crisprs_orphan.tab, and cas_operon_orphan.tab to combine, and due to the position (start, end) in the CRISPR_Cas.tab file is only for the cas operon, without the CRISPR array. To get the position of the CRISPR array you need to look in the crisprs_all.tab file*
*this part should be changed into code.*
```{r}

```
**The CCTyper output have `r ` defense systems in xx plasmids.**

---

### pre-combination: unite the defense type name, and data format.
```{r}

```

### Fin.