---
title: "PLSDB database dereplication"
author: "[Haotian Zheng](https://github.com/marveloushaotian)"
date: "`r Sys.Date()`"
output: html_document
---

**This document shows each level of PLSDB de-replication.**

**AccNb**: The **accurate** number of each kind of defense systems in plasmids.

**FreqNb**: The **Occ.** number of each kind of defense systems in plasmids (Each kind of defense systems only count once).

Use **top 10 abundance** defense systems as input.

1.  How many plasmids have 0/1/2/3/4/5... defense systems? (bar plot and pie chart)

2.  Among the plasmids with defense systems, what is the distribution of **AccNb** and the ratio.

------------------------------------------------------------------------

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE) # Need to change the path of the plot.

library(knitr) # evaluate the code, putting the results in a markdown document, which can then be converted to a variety of formats with pandoc.
library(tidyverse) # including ggplot2,dplyr,tidyr,readr,purrr,tibble,stringr,forcats.
# Matrix processing
library(reshape2) # 'melt', 'cast' rebuild database.
library(plyr)
library(data.table)

# Statistic.
library(scales) # generic function whose default method centers and/or scales the columns of a numeric matrix.
library(psych)
library(vegan)
library(randomForest)
library(caret)

# Visualization.
library(igraph)
library(ggrepel) # repel overlapping text labels.
library(ggthemes) # contains extra themes, scales, and geoms, and functions for and related to ggplot2.
library(ggpubr) # facilitates the creation of beautiful ggplot2-based graphs.
library(gg.gap) # Easy to define segments in y-axis for 'ggplot2'.
library(ggbreak) # Effectively Utilize Plotting Space to Deal With Large Datasets and Outliers.
library(RColorBrewer)
library(pheatmap) # A function to draw clustered heatmaps.
library(gggenes) # provides a 'ggplot2' geom and helper functions for draw- ing gene arrow maps.
library(gggenomes)

do.write <- F
options(scipen = 200)
```

### Import data.

```{r}
ratio <- read.table("../../Results/00.Original_Data/00.meta_data/dereplication_ratio.txt", header = T, check.names = F, sep = "\t")
```

------------------------------------------------------------------------

### Processed data.

```{r}
# Make the rate number in a numeric order.
ratio$dRep_ratio <- factor(ratio$dRep_ratio, levels = unique(ratio$dRep_ratio))
```

------------------------------------------------------------------------

### Visualization.

#### How many plasmids have 0/1/2/3/4/5... defense systems?

```{r}
ggplot(ratio,aes(x=dRep_ratio,y=Remain_plasmidsNb)) + 
  geom_line(aes(group=""), linetype="dotted", color="red", size=1) + 
  geom_point() +
  expand_limits(y=c(0, 40000)) +
  geom_text(aes(label=Remain_plasmidsNb),vjust = -0.2, hjust = 0.5,position = position_dodge2(width = 0.1, preserve = 'single')) + 
  labs(x="plasmids minium overlap", y="remain plasmids number") + 
  theme_bw() + 
  theme(plot.title = element_text(size = 20, face = "bold", angle = 0, vjust = 0.5, hjust = 0.5),
        axis.title.x = element_text(size = 15, face = "bold", angle = 0, vjust = 0.5, hjust = 0.5),
        axis.title.y = element_text(size = 15, face = "bold", angle = 90, vjust = 0.5, hjust = 0.5),
        axis.text.x = element_text(size = 10, face = "bold", angle = 0, vjust = 0.5, hjust = 0.5),
        axis.text.y = element_text(size = 10, face = "bold", angle = 0, vjust = 0.5, hjust = 0.5),
        legend.title = element_text(size = 15, face = "bold", angle = 0, vjust = 0.5, hjust = 0),
        legend.text = element_text(size = 12, face = "bold", angle = 0, vjust = 0.5, hjust = 0),
        legend.key = element_rect(fill = 'transparent'),
        legend.position = 'bottom',
        legend.key.size=unit(0.8,'cm'),
        legend.key.width=unit(1.2,'cm'),
        legend.spacing.y = unit(0.5,"cm"),
        # plot.margin = unit(c(1, 1, 1, 1),'cm'),
        strip.text.y = element_text(size=15,face = "bold"),
        strip.text.x = element_text(size=15,face = "bold")
        )
if(do.write){
  ggsave(width=6,height=6,filename="../../Results/00.Original_Data/00.meta_data/PLSDB_dRep.pdf",limitsize = FALSE)
}
```


Here is the meaning of the plot.

1.  We can see that the plasmids data is.

2.  


------------------------------------------------------------------------

### Fin.
