---
title: "System number - Plasmid size"
author: "[Haotian Zheng](https://github.com/marveloushaotian)"
date: "`r Sys.Date()`"
output: html_document
---

**This document analysis Distribution of defense systems number in different Plasmids size/Host bacteria size:**

**AccNb**: The **accurate** number of each kind of defense systems in plasmids.

**FreqNb**: The **Occ.** number of each kind of defense systems in plasmids (Each kind of defense systems only count once).

Use **top 10 abundance** defense systems as input.

1.  

2.  Among the plasmids with defense systems, what is the distribution of **AccNb** and the ratio.

3.  Among the plasmids with defense systems, what is the distribution of **AccNb** and the ratio that **normalized**.

4.  Among the plasmids with defense systems, what is the distribution of **FreqNb** and the ratio.

5.  What is the distribution of AccNb in **host**?

------------------------------------------------------------------------

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE) # Need to change the path of the plot.

library(knitr) # evaluate the code, putting the results in a markdown document, which can then be converted to a variety of formats with pandoc.
library(devtools)
library(tidyverse) # including ggplot2,dplyr,tidyr,readr,purrr,tibble,stringr,forcats.
# Matrix processing
library(reshape2) # 'melt', 'cast' rebuild database.
library(plyr)
library(data.table)

# Statistic.
library(scales) # generic function whose default method centers and/or scales the columns of a numeric matrix.
library(psych)
library(vegan)
library(randomForest)
library(caret)
library(mixtools)

# Visualization.
library(igraph)
library(ggrepel) # repel overlapping text labels.
library(ggthemes) # contains extra themes, scales, and geoms, and functions for and related to ggplot2.
library(ggpubr) # facilitates the creation of beautiful ggplot2-based graphs.
library(gg.gap) # Easy to define segments in y-axis for 'ggplot2'.
library(ggbreak) # Effectively Utilize Plotting Space to Deal With Large Datasets and Outliers.
library(RColorBrewer)
library(pheatmap) # A function to draw clustered heatmaps.
library(gggenes) # provides a 'ggplot2' geom and helper functions for draw- ing gene arrow maps.
library(gggenomes)
library(ggExtra)
library(COEF)

do.write <- F
options(scipen = 200)
```

#### Import data.

```{r}
metadata <- read.delim("../../Results/00.Original_Data/00.meta_data/plsdb_metadata_inuse.txt",header = T,check.names = F,sep = "\t")
combined_data2 <- read.table("../../Results/00.Original_Data/all_combined_data.txt",header = T,check.names = F,sep = "\t")
```

------------------------------------------------------------------------

#### Filter data.

------------------------------------------------------------------------

#### Visualization.

### The distribution of the defense system and plasmids genome with genome size.

### Plasmid Size - Plasmids number/Defence system number.

*how many plasmid have the same plasmid size range.* *how many system have the same plasmid size range.* *make the scales more details.* \# The plasmid size and the plasmids number and defence systems number.

```{r}
# combined_data3 <- combined_data2 %>% filter(combined_data2$Defense_System_Type == "ARGONAUTE")
combined_data3 <- combined_data2
combined_data4 <- combined_data3[,c(1,11)] %>% unique()


metadata2 <- metadata[,c(1,3)] %>% unique()

# diff_data <- setdiff(origin_metadata$ACC_NUCCORE,combined_data4$Plasmid_ID)
# combined_data5 <- origin_metadata %>% filter(origin_metadata$ACC_NUCCORE %in% diff_data)
# combined_data6 <- combined_data5[,c(1,13)] %>% unique()

ggplot(metadata2,aes(x=Length)) + 
  geom_density() +
  labs(x="Plasmids Size (Kb)", y="Density") + 
  theme_bw() + 
  scale_x_log10(labels = COEF::fancy_scientific) + 
  theme(plot.title = element_text(size = 20, face = "bold", angle = 0, vjust = 0.5, hjust = 0.5),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 15, face = "bold", angle = 90, vjust = 0.5, hjust = 0.5),
        axis.text.x = element_text(size = 15, face = "bold", angle = 0, vjust = 0.5, hjust = 0.5),
        axis.text.y = element_text(size = 13, face = "bold", angle = 0, vjust = 0.5, hjust = 0.5),
        legend.title = element_text(size = 15, face = "bold", angle = 0, vjust = 0.5, hjust = 0),
        legend.text = element_text(size = 12, face = "plain", angle = 0, vjust = 0.5, hjust = 0),
        legend.key = element_rect(fill = 'transparent'),
        legend.position = 'bottom',
        legend.key.size=unit(0.8,'cm'),
        legend.key.width=unit(1.2,'cm'),
        legend.spacing.y = unit(0.5,"cm"),
        # plot.margin = unit(c(1, 1, 1, 1),'cm'),
        strip.text.y = element_text(size=15,face = "bold"),
        strip.text.x = element_text(size=15,face = "bold")
)

if(do.write){
  ggsave(width=10,height=6,filename="../../Results/01.Distribution/plasmidsize_defense.pdf",limitsize = FALSE)
}
```

### normalize size plot. rate.

```{r}
combine_data <- read.table("../../Results/00.Original_Data/all_combined_data.txt",header = T,check.names = F,sep = "\t")
plsdb_ori <- read.delim2("../../Results/00.Original_Data/00.meta_data/plsdb_metadata_inuse.txt", header = T, check.names = F, sep = "\t")

with_systems <- combine_data[,c(1,2,11)]
# with_systems$mintag <- floor(with_systems$Length/10000)*10
with_systems$maxtag <- ceiling(with_systems$Length/1000)
with_systems$mintag <- ceiling(with_systems$Length/1000) - 1#0
with_systems$tag <- paste0(with_systems$mintag,"-",with_systems$maxtag) # the plasmids ID here have repeats cause need keep all systems number then we can count how many systems in a plasmids size group.

pre <- plsdb_ori %>% filter(plsdb_ori$Plasmid_ID %in% with_systems$Plasmid_ID) # select the plasmids which have the defense systems.
without_systems <- setdiff(plsdb_ori,pre)[,c(1,3)] # the plasmids have no defense system.
without_systems$Defense_System_Type <- "None"
# without_systems$mintag <- floor(without_systems$Length/10000)*10
without_systems$maxtag <- ceiling(without_systems$Length/1000)
without_systems$mintag <- ceiling(without_systems$Length/1000) - 1#0
without_systems$tag <- paste0(without_systems$mintag,"-",without_systems$maxtag)

with_systems_number <- tapply(with_systems$tag, with_systems$tag, length) %>% as.data.frame() %>% rownames_to_column("tag")
with_systems_number <- with_systems_number %>% dplyr::rename(defense_number=".")

with_systems_plasmids <- with_systems[,c(1,6)] %>% unique()
with_systems_plasmids_number <- tapply(with_systems_plasmids$tag,with_systems_plasmids$tag,length) %>% as.data.frame() %>% rownames_to_column("tag")
with_systems_plasmids_number <- with_systems_plasmids_number %>% dplyr::rename(plasmid_number=".")


without_systems_number <- tapply(without_systems$tag, without_systems$tag, length) %>% as.data.frame() %>% rownames_to_column("tag")
without_systems_number <- without_systems_number %>% dplyr::rename(defense_number=".")
without_systems_number$defense_number <- 0

without_systems_plasmids <- without_systems[,c(1,6)] %>% unique()
without_systems_plasmids_number <- tapply(without_systems_plasmids$tag, without_systems_plasmids$tag, length) %>% as.data.frame() %>% rownames_to_column("tag")
without_systems_plasmids_number <- without_systems_plasmids_number %>% dplyr::rename(plasmid_number=".")

combine_system_number <- rbind(with_systems_number,without_systems_number)
combine_system_plasmids_number <- rbind(with_systems_plasmids_number,without_systems_plasmids_number)

combine_system_number2 <- aggregate(defense_number ~ tag, data = combine_system_number, sum)
combine_system_plasmids_number2 <- aggregate(plasmid_number ~ tag, data = combine_system_plasmids_number, sum)

combine_new <- cbind(combine_system_number2,combine_system_plasmids_number2)[,c(1,2,4)]

combine_new$ratio <- round(combine_new$defense_number/combine_new$plasmid_number,5)
combine_new$split <- str_split_fixed(combine_new$tag,"-",2)[,1]
combine_new$split <- as.numeric(combine_new$split)

combine_new2 <- combine_new[order(combine_new$split),]

combine_new2$split <- factor(combine_new2$split,levels = unique(combine_new2$split))
combine_new2$tag <- factor(combine_new2$tag,levels = unique(combine_new2$tag))

combine_new3 <- combine_new2# %>% filter(combine_new2$ratio != 0)
combine_new4 <- combine_new3 %>% filter(combine_new3$plasmid_number >= 10)



combine_new4$split <- as.character(combine_new4$split)
combine_new4$split <- as.numeric(combine_new4$split)
# combine_new4$tag <- as.character(combine_new4$tag)

all_systems <- rbind(with_systems[,c(1,3,4,5,6)],without_systems[,c(1,2,4,5,6)]) %>% unique()
all_systems2 <- left_join(all_systems,combine_new2)

# all_systems3 <- all_systems2 %>% filter(all_systems2$ratio != 0)
all_systems3 <- all_systems2# %>% filter(all_systems2$plasmid_number >= 10) # Key point to remove all the group less then 10 plasmids.


all_systems3$split <- as.character(all_systems3$split)
all_systems3$split <- as.numeric(all_systems3$split)


p <- ggplot(all_systems3,aes(x=Length/1000,y=ratio)) +
  # geom_bar(fill="steelblue",stat = 'identity',width = 0.8) +
  geom_point() +
  geom_smooth(method="loess",se=T) +
  # geom_histogram(bins = split) + 
  scale_x_log10() +
  labs(x="Plasmids Size(Kb)", y="Ratio(System number/All Plasmids Number)") +
  theme_bw() +
  theme(plot.title = element_text(size = 20, face = "bold", angle = 0, vjust = 0.5, hjust = 0.5),
        axis.title.x = element_text(size = 15, face = "bold", angle = 0, vjust = 0.5, hjust = 0.5),
        axis.title.y = element_text(size = 15, face = "bold", angle = 90, vjust = 0.5, hjust = 0.5),
        axis.text.x = element_text(size = 10, face = "plain", angle = 0, vjust = 0.5, hjust = 0.5),
        axis.text.y = element_text(size = 10, face = "bold", angle = 0, vjust = 0.5, hjust = 0.5),
        legend.title = element_text(size = 15, face = "bold", angle = 0, vjust = 0.5, hjust = 0),
        legend.text = element_text(size = 12, face = "bold", angle = 0, vjust = 0.5, hjust = 0),
        legend.key = element_rect(fill = 'transparent'),
        legend.position = 'bottom',
        legend.key.size=unit(0.8,'cm'),
        legend.key.width=unit(1.2,'cm'),
        legend.spacing.y = unit(0.5,"cm"),
        # plot.margin = unit(c(1, 1, 1, 1),'cm'),
        strip.text.y = element_text(size=15,face = "bold"),
        strip.text.x = element_text(size=15,face = "bold")
        )
ggMarginal(p, type = "histogram", margins = "x", color = "black", fill="#00AFBB")
if(do.write){
  ggsave(width=6,height=7,filename="../../Results/01.Plasmids_system/SystemNb_per_Plasmids_nofilter.pdf",limitsize = FALSE)
}
```

------------------------------------------------------------------------

##### Fin.
